Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-15 paper/sheaf_lics.tex
begin formalization

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]#2{\ar@<-#2>[#1]\ar@<#2>[#1]} %double arrows in xy
\def\tar[#1]#2{\ar@<#2>[#1]\ar@<0pt>[#1]\ar@<-#2>[#1]} %triple arrows in xy
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\IsHProp}{IsHProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Contr}{Contr}
\DeclareMathOperator{\IsContr}{IsContr}
\DeclareMathOperator{\precompose}{\mathrm{precompose}}

@@

Then $P$ is the {\em colimit} of $D$ if for any other $X:\Type$, the
map
$$\lambda f:P \to X,~ \left( \lambda i,~f \circ q_i~;~ \lambda i\, j\,
  \phi,~ \precompose_f (p(i, j, g))) \right)$$
is an equivalence.

\nt{say what is $\precompose_f $}
\end{defi}

@@

>>>>

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]#2{\ar@<-#2>[#1]\ar@<#2>[#1]} %double arrows in xy
\def\tar[#1]#2{\ar@<#2>[#1]\ar@<0pt>[#1]\ar@<-#2>[#1]} %triple arrows in xy
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\IsHProp}{IsHProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Contr}{Contr}
\DeclareMathOperator{\IsContr}{IsContr}
\DeclareMathOperator{\postcompose}{\mathrm{postcompose}}

@@

Then $P$ is the {\em colimit} of $D$ if for any other $X:\Type$, the
map
$$\lambda f:P \to X,~ \left( \lambda i,~f \circ q_i~;~ \lambda i\, j\,
  \phi,~ \postcompose_f (p(i, j, g))) \right),$$
where $\postcompose_f : \phi = \psi \to \phi \circ f = \psi \circ f$,
is an equivalence.
\end{defi}

@@

Formalisation of subobject classifiers has been done in
\texttt{sub\_object\_classifier.v}, 284 lines.

Colimits, $p$-pullbacks and \v{C}ech nerves has been formalized in
\texttt{colimits.v, cech\_nerve.v}, 552 lines.

Reflective subuniverses and modalities are formalized in
\texttt{reflective\_subuniverse.v, modalities.v}, 1053 lines.

Definition of th reflective subuniverse on $\HProp$ is given in
\texttt{sheaf\_base\_case.v}, 186 lines.

Section~\ref{sec:sheaves} is formalized in
\texttt{sheaf\_def\_and\_thm.v}, 1029 lines.

Section~\ref{sec:sheafification} is formalized in
\texttt{sheaf\_induction.v}, 2340 lines.

At total, with other files containing technical lemmas, the project
contains 6322 lines.
